EGGs are adhesive!

### 2025-03-12 calco/main.tex
minima
Term graphs with closed eq

\noindent
\begin{minipage}[l]{.73\linewidth}
\begin{definition}
An \emph{algebraic signature} $\Sigma$ is a pair $(O_\Sigma, \ari_\Sigma)$ given by a \emph{set of operations} $O_\Sigma$ and an \emph{arity function} $\ari_\Sigma\colon O_\Sigma \to \mathbb{N}$. 
%
We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $\{1\}$ as set of nodes, so that $\{1\}^\star$ is $\mathbb{N}$, $\ari_\sigma$ as the source function and $\delta_1$ as target function, which always picks the element $1$. The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
\end{definition}

@@

\begin{restatable}{corollary}{mn}\label{cor:mono2}
	An arrow $(h_E, h_V, h_Q): \mathcal{G\to H}$ in $\EqHyp$ is a regular mono if and only if all its components are injective functions.
\end{restatable}\todo{manca ancora la dimostrazione dell'implicazione da destra a sinistra}

@@

                &\emptyset \ar@{>->}[dd]|\hole_(.65){a}\ar@{>->}[rr]^{v} \ar@{>->}[dl]_{u} &&

@@

                \end{tikzpicture} \ar@{>->}[dd]^{b} \ar@{>->}[dl]_{y} \\

@@

                \ar@{>->}[dd]_{c}\ar@{>->}[rr]^(.7){z} & &

@@

                \ar@{>->}[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && 

@@

\subsection{Term graphs with closed equivalence}
\todo{Here we must introduce $\GEqTGs$}

>>>>

\noindent
\begin{minipage}[l]{.73\linewidth}
\begin{definition}
An \emph{algebraic signature} $\Sigma$ is a pair $(O_\Sigma, \ari_\Sigma)$ given by a \emph{set of operations} $O_\Sigma$ and an \emph{arity function} $\ari_\Sigma\colon O_\Sigma \to \mathbb{N}$. 
%
We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $\{1\}$ as set of nodes, so that $\{1\}^\star$ is $\mathbb{N}$, $\ari_\Sigma$ as the source function and $\delta_1$ as target function, which always picks the element $1$. The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
\end{definition}

@@

\begin{restatable}{corollary}{mn}\label{cor:mono2}
	An arrow $(h_E, h_V, h_Q): \mathcal{G\to H}$ in $\EqHyp$ is a regular mono if and only if all its components are injective functions.
\end{restatable}

@@

                &\emptyset \ar@{>->}[dd]|\hole \ar@{>->}[rr] \ar@{>->}[dl] &&

@@

                \end{tikzpicture} \ar@{>->}[dd] \ar@{>->}[dl] \\

@@

                \ar@{>->}[dd]\ar@{>->}[rr] & &

@@

                \ar@{>->}[rr]|\hole \ar@{>->}[dl] && 

@@

\subsection{Term graphs with closed equivalence}

\begin{remark}\label[remark]{sig_egg}
	Given a signature $\Sigma = (O_\Sigma, \ari_\Sigma)$,
	the hypergraph 
	$R(\mathcal{G}^\Sigma) = (O_\Sigma, 1, 1, \ari_\Sigma, \delta_1, \id{1})$
	is an object of $\egg$.
	Indeed, if $(S, \pi_1, \pi_2)$ is the kernel pair of $\id{1}^\star \circ \ari_\Sigma$,
	we have that $\id{1}^\star \circ \delta_1 \circ \pi_1$ and $\id{1}^\star \circ \delta_1 \circ \pi_2$ are both the contant functions of value $1$.
\end{remark}

\begin{definition}\label[definintion]{def:GEqTGs}
	Given a signature $\Sigma$, we define the category $\GEqTGs$ as the full subcategory of $\egg/R(\mathcal{G}^\Sigma)$ in which objects are arrows $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ where $t_\mathcal{G}$ is mono. The incusion functor is denoted $I_{\GEqTGs} : \GEqTGs \to \egg/R(\mathcal{G}^\Sigma)$.
\end{definition}

\todo{Here we must introduce $\GEqTGs$}
